Patchwork: Incremental Computation for Static Analysis

### 2018-12-10 paper.tex
update paper draft based on 12-3 discussion

Parity analysis (requires lattice)\\
Interval analysis (requires widening)

\section{Approach: fungilang + lattice?}

Present fungilang semantics

@@

Analyses:\\
Simple interval? Points-to? Interprocedural?

Programs:\\
IncA benchmarks? Flix benchmarks? Both?

Edit model:\\
Adopt IncA approach? Commit history? Other?

We compare to {Flix/IncA}?

>>>>

Parity analysis (requires lattice)\\
Interval analysis (requires widening)\\
Octagon analysis (relational)

\section{Contribution: Incremental Relation Structures}

We developed an incremental data structure to represent the abstract states necessary to back our static analyses. It is...

\section{Contribution: Extending to Incremental Analysis Framework}

We use the discussed data structures in a modular framework for implementing static analyses. Our framework is organized as follows...

@@

Analyses:\\
Interval, octagon.

Programs:\\
IncA benchmarks?

Edit model:\\
Adopt IncA approach?

We compare to: IncA, off-the-shelf analysis?

We show: same alarm rates as off-the-shelf analysis, similar incremental performance as IncA. QoIs: cumulative time, alarm rates, false alarm rates

We need: off-the-shelf analysis to use, benchmarks to use, edit model to use
